Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking

### 2021-01-14 博士/论文提交/adversarial_attack/IJCAI/FormattingGuidelines-IJCAI-21/main.tex
隐去作者
更新 introduction

\author{
Zhenbang Li$^1$\and
Jin Gao$^2$\footnote{Corresponding Author}\and
YaYa Shi$^{2,3}$\and
Bing Li$^4$\and
Pengpeng Liang$^5$\And
Weiming Hu$^6$\\
\affiliations
$^1$First Affiliation\\
$^2$Second Affiliation\\
$^3$Third Affiliation\\
$^4$Fourth Affiliation\\
\emails
\{first, second\}@example.com,
third@other.example.com,
fourth@example.com
}

@@

>>>>

\iffalse
\author{
Zhenbang Li$^1$\and
Jin Gao$^2$\footnote{Corresponding Author}\and
YaYa Shi$^{2,3}$\and
Bing Li$^4$\and
Pengpeng Liang$^5$\And
Weiming Hu$^6$\\
\affiliations
$^1$First Affiliation\\
$^2$Second Affiliation\\
$^3$Third Affiliation\\
$^4$Fourth Affiliation\\
\emails
\{first, second\}@example.com,
third@other.example.com,
fourth@example.com
}
\else
\author{PaperID: 2266}
\fi

@@

All the above methods can fool object trackers successfully. However, these attack methods are not suitable for the real-world online-tracking phase where we can not get access to the limited computational resources.
The reason is, visual object tracking is a computationally intensive task which usually needs to be run in real time, but the computational source of small platforms (e.g., mobile, robotic, self-driving car) used to deploy the trackers is often limited.
Therefore, the attack approaches for object tracking should occupy as little computing resources as possible.
But the reality is that most attack algorithms either perform iterative optimisation to calculate adversarial examples, or generate perturbations through Generative Adversarial Networks which occupy the GPU memory.
